---
title: "Hudson"
author: "Maxwel Coura Oliveira"
date: "10/12/2020"
output: html_document
---

# Load the packages 😁

```{r include=FALSE}
library(tidyverse) # pacote dos graficos e manipulacao dos dados etc
library(drc) # pacote da dose resposta
library(skimr)
```

# Importa dataset

```{r}
data <- read_csv("ic50.csv") # importando os dados
# apareceu um aviso que 2 colunas estao duplicadas (mesmo nome)
```

# Data manipulation

```{r}
# manipulacao de dados
new_dt <- data %>% 
   pivot_longer(cols = 3:30, # juntando todos herbicidas em 1 coluna
                names_to = "herbicide", # nome da coluna
                values_to = "resp") %>% # valores varial resposta
  mutate_if(is.character, as.factor) %>%  # passando herbicide para factor
  mutate(resp = round(resp, 2), # 2 casas decimais para a resp
         dose = round(dose, 0)) # casas decimais 0 para dose
```

# Data view

```{r}
glimpse(new_dt) # olhando seus dados
```

```{r}
skim(new_dt) # outra forma de visulizar seus dados
```

# Data visualization

```{r}
new_dt %>% 
  ggplot(aes(x=dose, y=resp, color=herbicide)) + 
  geom_point(show.legend = FALSE)
```

# Modeling

## Using l4 (logistic with 4 parameter)

```{r warning=FALSE}
# Fazendo um modelo unico para todos os herbicidas
# usei a funcao l4
model <- drm(resp ~ dose, herbicide, fct=l4(fixed = c(NA, NA, NA, NA), names = c("slope", "lower", "upper", "ed50")), data = new_dt)
summary(model)
```

## Checking the other models

```{r warning=FALSE}
# Vamos testar qual funcao sairia melhor com esses dados
# Selecionei os principais modelos na lista
mselect(model, fctList = list(W2.3(), W1.3(), l3(),  W1.4(), W2.4(), L.4(), LL.4()), nested = FALSE,
sorted = c("IC", "Res var", "Lack of fit", "no"), linreg = FALSE, icfct = AIC)
# resultado mostra que W1.3() eh a melhor opcao
```

## Using W1.3

Weibull logistic model with 3 parameter

```{r  warning=FALSE}
model2 <- drm(resp ~ dose, herbicide, fct=W1.3(fixed = c(NA, NA, NA), names = c("slope", "upper", "ed50")), data = new_dt)
summary(model2)

# Alguns herbicidas nao estao convergindo (12763099 e 12769961)! Veja a quantidade de parametros com NAs. 
```

I am trying to fit 28 herbicides in a single. It is likely that some will not converge. Because I am fitting all herbicides in a single model, I am removing three herbicides that is showing NAs in parameters. See the next step.

## Fitting again

Weibull logistic model with 3 parameter. I have removed 3 herbicides that did not converge.

```{r  warning=FALSE}
new_dt_2 <- new_dt %>% # new dataset to remove 3 herbicides
  filter(herbicide != "12763099" &
         herbicide != "12769961" &
         herbicide !=  "12690527")

model_3 <- drm(resp ~ dose, herbicide, fct=W1.3(fixed = c(NA, NA, NA), names = c("slope", "upper", "ed50")), data = new_dt_2)
summary(model_3)
```

## EDs

Effective dose that matches the 50% and 90% in your y-axis. Pay attention to the absolute or relative values.

```{r}
ED(model_3, c(50,90), type="absolute", interval = "delta")
# type = absolute eh pq ta mostrando o 50% no eixo y / se colocar "relative" vai mostrar relativo ao upper limit de cada herbicida
```

## Comparing EDs 50

```{r}
# t-test comparando as ED50 de cada herbicida
EDcomp(model_3, c(50,50), type="absolute", interval = "delta")
# type = absolute mesmo sentido do que foi explicado
```

# Data visualization

## Data preparation

Drc package is still not easy to work with ggplot (the best data viz package). We need to do some work arounds before plotting.

```{r Control prediction, include=FALSE}
newdata <- expand.grid(dose=exp(seq(log(0.5), log(1000), length=1000)))

newdata1 <- data.frame(herbicide =c("12692543"), newdata)
newdata2 <- data.frame(herbicide =c("12692555"), newdata)
newdata3 <- data.frame(herbicide =c("12432815"), newdata)
newdata4 <- data.frame(herbicide =c("12692547"), newdata)
newdata5 <- data.frame(herbicide =c("12665563"), newdata)
newdata6 <- data.frame(herbicide =c("12769963"), newdata)
newdata7 <- data.frame(herbicide =c("12771723"), newdata)
newdata8 <- data.frame(herbicide =c("6605"), newdata)
newdata9 <- data.frame(herbicide =c("6665"), newdata)
newdata10 <- data.frame(herbicide =c("139324"), newdata)
newdata11 <- data.frame(herbicide =c("651869"), newdata)
newdata12 <- data.frame(herbicide =c("654755"), newdata)
newdata13 <- data.frame(herbicide =c("12321045"), newdata)
newdata14 <- data.frame(herbicide =c("12721871"), newdata)
newdata15 <- data.frame(herbicide =c("669329"), newdata)
newdata16 <- data.frame(herbicide =c("12640095"), newdata)
newdata17 <- data.frame(herbicide =c("12771723_1"), newdata)
newdata18 <- data.frame(herbicide =c("12778693"), newdata)
newdata19 <- data.frame(herbicide =c("12771019"), newdata)
newdata20 <- data.frame(herbicide =c("12771021"), newdata)
newdata21 <- data.frame(herbicide =c("12718827"), newdata)
newdata22 <- data.frame(herbicide =c("12775311"), newdata)
newdata23 <- data.frame(herbicide =c("659292"), newdata)
newdata24 <- data.frame(herbicide =c("12771021_1"), newdata)
newdata25 <- data.frame(herbicide =c("156054"), newdata)


nd=rbind(newdata1, newdata2, newdata3, newdata4, newdata5, 
         newdata6, newdata7, newdata8, newdata9, newdata10,
         newdata11, newdata12, newdata13, newdata14, newdata15,
         newdata16, newdata17, newdata18, newdata19, newdata20,
         newdata21, newdata22, newdata23, newdata24, newdata25
         )
pm <- predict(model_3, newdata=nd, interval="confidence")

nd$p <- pm[,1] 
nd$pmin <- pm[,2] 
nd$pmax <- pm[,3] 

new_dt_2$dose0 <- new_dt_2$dose
new_dt_2$dose0[new_dt_2$dose0==0] <- 0.5
```

## Plotting the model

```{r Control Plot, message=FALSE, warning=FALSE}
ggplot(new_dt_2, aes(x = dose, y = resp, color=herbicide)) +    
  geom_line(data=nd, aes(x=dose, y=p), size=1.3) +
  labs(fill="", y="response", x=expression(bold(paste("Herbicide (g ai ha "^"-1",")")))) +
  scale_x_continuous(breaks=c(1, 10, 100, 1000, 10000)) + 
  coord_trans(x="log") +
  theme(axis.text=element_text(size=12, color="black"), 
        axis.title=element_text(size=16, face="bold"), 
        panel.background = element_rect(fill="white", color = "black"), 
        panel.grid.major = element_line(color = "white"), 
        panel.grid.minor = element_blank(),
        legend.key.width = unit(1, "line"),
        legend.position=c(0.15, 0.2), 
        legend.text = element_text(size = 8, colour = "black"), 
        legend.key = element_rect(fill=NA),           
        panel.border=element_rect(fill=NA, color="black", size=0.7, 
                                  linetype = "solid"), 
        legend.background = element_rect(fill =NA),      
        legend.title=element_blank()) + #ylim(0,100) +
   ggsave("figure.png", units="in", width=10, height=10, dpi=300)
```

# Fitting the removed models

## New dataset

```{r}
new_dt_3 <- new_dt %>% # new dataset witg 3 herbicides removed
  filter(herbicide == "12763099" |
         herbicide == "12769961" |
         herbicide ==  "12690527")
```

# New model

```{r warning=FALSE}
model_4 <- drm(resp ~ dose, herbicide, fct=W1.3(fixed = c(NA, NA, NA), names = c("slope", "upper", "ed50")), data = new_dt_2)
summary(model_4)
```

See here that your removed models converged well. It was not converging before because the amount of herbicides.

# New analysis

I have done this one here just to you see all herbicides individually.

```{r}
# Nesting data
nested_data <- new_dt %>% 
  group_by(herbicide) %>% 
  nest()
nested_data
```

```{r warning=FALSE}
# Fitting linear models
drc_models <- nested_data %>% 
  mutate(models = map(data, ~ drm(resp ~ dose, fct=W1.3(), data = .x)))
drc_models
```

```{r warning=FALSE}
drc_models %>% 
  mutate(plots = map(models, plot))
```
